VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-09-23 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added inverse procedure theorem

\begin{theorem}
\label{t:conv}
The following Cavalieri, Riemann, and Riemann--Stieltjes integrals are equivalent
\begin{equation}
\int_{a(y)}^{b(y)} f(x) dx = \int_a^b f\circ h(x) dx = \int_{a'}^{b'} f(x)dg(x). 
\end{equation}
\end{theorem}

@@

The area of $R$ can be approximated by summing together the area of rectangular integrations strips that inscribe $R$. There, however, exist a more 
straightforward way in which we can approximate the area of $R$: we can sum together the area of non-rectangular integration strips inscribing $R$. This alternative approach 
will only succeed it the sides of the aforementioned integration strips are all tranlsations of the function $a(y)$.

>>>>

\begin{theorem}
\label{t:conv}
The following Cavalieri, Riemann, and Riemann--Stieltjes integrals are equivalent
\begin{equation}
\int_{a(y)}^{b(y)} f(x) dx = \int_a^b f\circ h(x) dx = \int_{a'}^{b'} f(x)dg(x). 
\end{equation}
\end{theorem}
\begin{theorem}
Let $\widetilde{g}(x)$ and $f(x)$ be known (continious) invertable real-valued functions. Moreover, let $a'\in \mathbb{R}$ and $b'\in \mathbb{R}$.  If $f^{-1}(0) - \widetilde{g}\circ f^{-1}(0) + g(a')$ exists then there exists a unique 
$C\in\mathbb{R}$ such that 
\begin{equation}
\int_{a'}^{b'} f(x)~dg(x) = \int_{a(y)}^{b(y)} f(x)~dx, 
\end{equation}
where $g(x) = \widetilde{g}(x) + C$ and $a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a')$.
\end{theorem}

@@

It seems much more straightforward to approximate the area of $R$ via non-overlapping non-rectangular integration strips that toghether inscribe $R$ than having to 
rectangular integration strips. This alternative approach 
will only succeed it the sides of the aforementioned integration strips are all tranlsations of the function $a(y)$.
